Online Multiclass Linear Classification with Bandit Feedback

### 2019-01-18 ICML-submission/algorithm-for-strongly-linearly-separable-data.tex
nn alg

\paragraph{Remark.} Irrespective of any conditions on $K$, $R$, and $\gamma$, a
trivial lower bound on the expected number of mistakes of any randomized
algorithm is $\frac{K-1}{2}$. To see this, note that the adversary can choose an
example $(R e_1, y)$, where $y$ is a label chosen uniformly from
$\cbr{1,2,\dots,K}$, and show this example $K$ times. The sequence of examples
trivially satisfies the strong linear separability condition, and the
$\frac{K-1}{2}$ expected mistake lower bound follows from Claim 2
of~\citet{Daniely-Helbertal-2013}. However, it is unclear if the trivial lower
bound is the best possible if $K$ is large, i.e., $\omega((R/\gamma)^2)$. We
leave this as an open problem.

>>>>

\paragraph{Remark.} Irrespective of any conditions on $K$, $R$, and $\gamma$, a
trivial lower bound on the expected number of mistakes of any randomized
algorithm is $\frac{K-1}{2}$. To see this, note that the adversary can choose an
example $(R e_1, y)$, where $y$ is a label chosen uniformly from
$\cbr{1,2,\dots,K}$, and show this example $K$ times. The sequence of examples
trivially satisfies the strong linear separability condition, and the
$\frac{K-1}{2}$ expected mistake lower bound follows from ~\citep[][Claim 2]{Daniely-Helbertal-2013}. However, it is unclear if the trivial lower
bound is the best possible if $K$ is large, i.e., $\omega((R/\gamma)^2)$. We
leave this as an open problem.
